MRD_final_microbiome

### 2019-06-26 import_popln_data.Rmd
updated

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory
mnd.incidence <- as.data.frame(read_csv("MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("MND-P-B.csv",col_names = TRUE))
mnd.incidence <- mb.gather(mnd.incidence)
mnd.prev <- mb.gather(mnd.prev)

>>>>

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory

# For MND
mnd.incidence <- as.data.frame(read_csv("./rawdata/MND-I-B.csv",col_names = TRUE))

mnd.i.12 <- as.data.frame(read_csv("./rawdata/MND-I-B-12.csv",col_names = TRUE))
mnd.i.13 <- as.data.frame(read_csv("./rawdata/MND-I-B-13.csv",col_names = TRUE))
mnd.i.14 <- as.data.frame(read_csv("./rawdata/MND-I-B-14.csv",col_names = TRUE))
mnd.i.15 <- as.data.frame(read_csv("./rawdata/MND-I-B-15.csv",col_names = TRUE))
mnd.i.16 <- as.data.frame(read_csv("./rawdata/MND-I-B-16.csv",col_names = TRUE))

mnd.prev <- as.data.frame(read_csv("./rawdata/MND-P-B.csv",col_names = TRUE))
mnd.p.12 <- as.data.frame(read_csv("./rawdata/MND-P-B-12.csv",col_names = TRUE))
mnd.p.13 <- as.data.frame(read_csv("./rawdata/MND-P-B-13.csv",col_names = TRUE))
mnd.p.14 <- as.data.frame(read_csv("./rawdata/MND-P-B-14.csv",col_names = TRUE))
mnd.p.15 <- as.data.frame(read_csv("./rawdata/MND-P-B-15.csv",col_names = TRUE))
mnd.p.16 <- as.data.frame(read_csv("./rawdata/MND-P-B-16.csv",col_names = TRUE))

mnd.roc.i <- as.data.frame(read_csv("./rawdata/MND-I-B-RoC.csv",col_names = TRUE))

mnd.roc.p <- as.data.frame(read_csv("./rawdata/MND-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
mnd.incidence <- mb.gather(mnd.incidence)
colnames(mnd.incidence)[2] <- "incidence 2017"

mnd.i.12 <- mb.gather(mnd.i.12)
colnames(mnd.i.12)[2] <- "incidence 2012"
mnd.i.13 <- mb.gather(mnd.i.13)
colnames(mnd.i.13)[2] <- "incidence 2013"
mnd.i.14 <- mb.gather(mnd.i.14)
colnames(mnd.i.14)[2] <- "incidence 2014"
mnd.i.15 <- mb.gather(mnd.i.15)
colnames(mnd.i.15)[2] <- "incidence 2015"
mnd.i.16 <- mb.gather(mnd.i.16)
colnames(mnd.i.16)[2] <- "incidence 2016"
mnd.roc.i <- mb.gather(mnd.roc.i)
colnames(mnd.roc.i)[2] <- "ROC incidence"

mnd.prev <- mb.gather(mnd.prev)
colnames(mnd.prev)[2] <- "prevalance 2017"
mnd.p.12 <- mb.gather(mnd.p.12)
colnames(mnd.p.12)[2] <- "prevalance 2012"
mnd.p.13 <- mb.gather(mnd.p.13)
colnames(mnd.p.13)[2] <- "prevalance 2013"
mnd.p.14 <- mb.gather(mnd.p.14)
colnames(mnd.p.14)[2] <- "prevalance 2014"
mnd.p.15 <- mb.gather(mnd.p.15)
colnames(mnd.p.15)[2] <- "prevalance 2015"
mnd.p.16 <- mb.gather(mnd.p.16)
colnames(mnd.p.16)[2] <- "prevalance 2016"
mnd.roc.p <- mb.gather(mnd.roc.p)
colnames(mnd.roc.p)[2] <- "ROC prevalance"

# Join them together.

mnd.i <- list( mnd.i.12, mnd.i.13,mnd.i.14,mnd.i.15,mnd.i.16,mnd.incidence,mnd.roc.i) %>% reduce(left_join, by = "Location")

mnd.p <- list( mnd.p.12, mnd.p.13,mnd.p.14,mnd.p.15,mnd.p.16,mnd.incidence,mnd.roc.p) %>% reduce(left_join, by = "Location")

# For IPD

ipd.incidence <- as.data.frame(read_csv("./rawdata/PD-I-B.csv",col_names = TRUE))

ipd.i.12 <- as.data.frame(read_csv("./rawdata/PD-I-B-12.csv",col_names = TRUE))
ipd.i.13 <- as.data.frame(read_csv("./rawdata/PD-I-B-13.csv",col_names = TRUE))
ipd.i.14 <- as.data.frame(read_csv("./rawdata/PD-I-B-14.csv",col_names = TRUE))
ipd.i.15 <- as.data.frame(read_csv("./rawdata/PD-I-B-15.csv",col_names = TRUE))
ipd.i.16 <- as.data.frame(read_csv("./rawdata/PD-I-B-16.csv",col_names = TRUE))

ipd.prev <- as.data.frame(read_csv("./rawdata/PD-P-B.csv",col_names = TRUE))
ipd.p.12 <- as.data.frame(read_csv("./rawdata/PD-P-B-12.csv",col_names = TRUE))
ipd.p.13 <- as.data.frame(read_csv("./rawdata/PD-P-B-13.csv",col_names = TRUE))
ipd.p.14 <- as.data.frame(read_csv("./rawdata/PD-P-B-14.csv",col_names = TRUE))
ipd.p.15 <- as.data.frame(read_csv("./rawdata/PD-P-B-15.csv",col_names = TRUE))
ipd.p.16 <- as.data.frame(read_csv("./rawdata/PD-P-B-16.csv",col_names = TRUE))

ipd.roc.i <- as.data.frame(read_csv("./rawdata/PD-I-B-RoC.csv",col_names = TRUE))

ipd.roc.p <- as.data.frame(read_csv("./rawdata/PD-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
ipd.incidence <- mb.gather(ipd.incidence)
colnames(ipd.incidence)[2] <- "incidence 2017"

ipd.i.12 <- mb.gather(ipd.i.12)
colnames(ipd.i.12)[2] <- "incidence 2012"
ipd.i.13 <- mb.gather(ipd.i.13)
colnames(ipd.i.13)[2] <- "incidence 2013"
ipd.i.14 <- mb.gather(ipd.i.14)
colnames(ipd.i.14)[2] <- "incidence 2014"
ipd.i.15 <- mb.gather(ipd.i.15)
colnames(ipd.i.15)[2] <- "incidence 2015"
ipd.i.16 <- mb.gather(ipd.i.16)
colnames(ipd.i.16)[2] <- "incidence 2016"
ipd.roc.i <- mb.gather(ipd.roc.i)
colnames(ipd.roc.i)[2] <- "ROC incidence"

ipd.prev <- mb.gather(ipd.prev)
colnames(ipd.prev)[2] <- "prevalance 2017"
ipd.p.12 <- mb.gather(ipd.p.12)
colnames(ipd.p.12)[2] <- "prevalance 2012"
ipd.p.13 <- mb.gather(ipd.p.13)
colnames(ipd.p.13)[2] <- "prevalance 2013"
ipd.p.14 <- mb.gather(ipd.p.14)
colnames(ipd.p.14)[2] <- "prevalance 2014"
ipd.p.15 <- mb.gather(ipd.p.15)
colnames(ipd.p.15)[2] <- "prevalance 2015"
ipd.p.16 <- mb.gather(ipd.p.16)
colnames(ipd.p.16)[2] <- "prevalance 2016"
ipd.roc.p <- mb.gather(ipd.roc.p)
colnames(ipd.roc.p)[2] <- "ROC prevalance"

# Join them together.

ipd.i <- list( ipd.i.12, ipd.i.13,ipd.i.14,ipd.i.15,ipd.i.16,ipd.incidence,ipd.roc.i) %>% reduce(left_join, by = "Location")

ipd.p <- list( ipd.p.12, ipd.p.13,ipd.p.14,ipd.p.15,ipd.p.16,ipd.incidence,ipd.roc.p) %>% reduce(left_join, by = "Location")

# For AD

ad.incidence <- as.data.frame(read_csv("./rawdata/AD-I-B.csv",col_names = TRUE))

ad.i.12 <- as.data.frame(read_csv("./rawdata/AD-I-B-12.csv",col_names = TRUE))
ad.i.13 <- as.data.frame(read_csv("./rawdata/AD-I-B-13.csv",col_names = TRUE))
ad.i.14 <- as.data.frame(read_csv("./rawdata/AD-I-B-14.csv",col_names = TRUE))
ad.i.15 <- as.data.frame(read_csv("./rawdata/AD-I-B-15.csv",col_names = TRUE))
ad.i.16 <- as.data.frame(read_csv("./rawdata/AD-I-B-16.csv",col_names = TRUE))

ad.prev <- as.data.frame(read_csv("./rawdata/AD-P-B.csv",col_names = TRUE))
ad.p.12 <- as.data.frame(read_csv("./rawdata/AD-P-B-12.csv",col_names = TRUE))
ad.p.13 <- as.data.frame(read_csv("./rawdata/AD-P-B-13.csv",col_names = TRUE))
ad.p.14 <- as.data.frame(read_csv("./rawdata/AD-P-B-14.csv",col_names = TRUE))
ad.p.15 <- as.data.frame(read_csv("./rawdata/AD-P-B-15.csv",col_names = TRUE))
ad.p.16 <- as.data.frame(read_csv("./rawdata/AD-P-B-16.csv",col_names = TRUE))

ad.roc.i <- as.data.frame(read_csv("./rawdata/AD-I-B-RoC.csv",col_names = TRUE))

ad.roc.p <- as.data.frame(read_csv("./rawdata/AD-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
ad.incidence <- mb.gather(ad.incidence)
colnames(ad.incidence)[2] <- "incidence 2017"

ad.i.12 <- mb.gather(ad.i.12)
colnames(ad.i.12)[2] <- "incidence 2012"
ad.i.13 <- mb.gather(ad.i.13)
colnames(ad.i.13)[2] <- "incidence 2013"
ad.i.14 <- mb.gather(ad.i.14)
colnames(ad.i.14)[2] <- "incidence 2014"
ad.i.15 <- mb.gather(ad.i.15)
colnames(ad.i.15)[2] <- "incidence 2015"
ad.i.16 <- mb.gather(ad.i.16)
colnames(ad.i.16)[2] <- "incidence 2016"
ad.roc.i <- mb.gather(ad.roc.i)
colnames(ad.roc.i)[2] <- "ROC incidence"

ad.prev <- mb.gather(ad.prev)
colnames(ad.prev)[2] <- "prevalance 2017"
ad.p.12 <- mb.gather(ad.p.12)
colnames(ad.p.12)[2] <- "prevalance 2012"
ad.p.13 <- mb.gather(ad.p.13)
colnames(ad.p.13)[2] <- "prevalance 2013"
ad.p.14 <- mb.gather(ad.p.14)
colnames(ad.p.14)[2] <- "prevalance 2014"
ad.p.15 <- mb.gather(ad.p.15)
colnames(ad.p.15)[2] <- "prevalance 2015"
ad.p.16 <- mb.gather(ad.p.16)
colnames(ad.p.16)[2] <- "prevalance 2016"
ad.roc.p <- mb.gather(ad.roc.p)
colnames(ad.roc.p)[2] <- "ROC prevalance"

# Join them together.

ad.i <- list( ad.i.12, ad.i.13,ad.i.14,ad.i.15,ad.i.16,ad.incidence,ad.roc.i) %>% reduce(left_join, by = "Location")

ad.p <- list( ad.p.12, ad.p.13,ad.p.14,ad.p.15,ad.p.16,ad.incidence,ad.roc.p) %>% reduce(left_join, by = "Location")
